Datasheet for Children's Book Ratings

### 2023-03-25 outputs/paper/paper.qmd
Added in-text citations and introduction
Completed Motivation section of datasheet

I follow the recommendations of [@gebru2021datasheets].

@@

-   **For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.**
-   **Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?**
-   **Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.**
-   **Any other comments?**
    -   No

>>>>

The dataset of interest is Alex Cookson's data on the ratings of children's books [@alexcookson_childrensbookratings]. For the datasheet of this dataset, I follow the recommendations of Gebru [@gebru2021datasheets].

@@

-   **For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.**
    -   The dataset was created to address the problem of inconsistency on rating sites and to estimate more reasonable ratings, specifically for children's books by using empirical Bayes estimation.
-   **Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?**
    -   Alex Cookson, while working at the Royal Canadian Mint.
-   **Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.**
    -   No direct funding was received for this project.
-   **Any other comments?**
    -   No.
